### 2016-01-26 hans/bayes-tardis-luminosity-prediction.tex
[hans] dos2unix line endings cleanup
[draft] Start Gamma section

@@

>>>>

\DeclareMathOperator{\GammaDist}{Gamma}

@@

\subsection{Results for the Gamma-distribution likelihood}

The Gamma distribution is with shape parameter $\alpha$ and rate
parameter $\beta$ is defined as
\begin{align}
  \lleq{gma}
  p(x | \alpha, \beta) = \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x} .
\end{align}
For our purposes, the most important property is that the Gamma distribution is infinitely divisible; i.e., the sum of $N$ Gamma variates is again a Gamma variate
\begin{align}
  \lleq{gmb}
  X_i \sim Gamma(\alpha, \beta) \Rightarrow \sum_{i=1}^N X_i \sim Gamma(N \alpha, \beta)
\end{align}
